Beyond query expansion - expanding documents for fluid keyword search

### 2020-10-09 IUI2021/paper.tex
...

  We have been using this document expansion technique called
  ExpandSearch for several years, and the system is working on various
  commercial Web services. In this paper, we describe the idea and
  implementation of ExpandHelp and show how it works in the wild.
\end{abstract}

@@

People are frequently searching information using keywords on Google
and other systems, but keyword search is still not an easy task,
because it is fundamentally difficulto to find appropriate information
that does not contain the keyword given by the user.

@@

The help system of MacOS (Catalina v10.15.5) does not tell a user how to remove a file.

\begin{figure}[H]
  \centering
  \includegraphics[width=10cm,bb=0 0 1290 1090]{figures/eaa80e41ddc3d3620fae133007274573.png}
  \caption{Asking the help application how to remove a file.}
  \Description{Mac Mac}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=10cm,bb=0 0 1310 1090]{figures/0cd679128d8f69eb2a8a966d6466a8a4.png}
  \caption{Mac}
  \Description{Mac Mac}
\end{figure}

We can get this kind of information fairly easily using search systems on Internet,
so many people prefer getting information using search engines rather than
using help systems provided by manufacturers.

We can find information on Google because there are tremendous information
that describe how to ``remove a file'' on Mac.
If there are documens that contain ``remove'', ``file'', and ``Mac'',
finding such documents are not easy.

That seems to be the main reason why people are satisfied with search engines on the net
for finding popular? information.

@@

On the other hand,
finding a less popular information is rather difficult,
because not enough document related to the topic is found on the net.

If there is only one document on the net
that describes the \texttt{console} feature of a minor system \texttt{xxxxx},
people cannot find the document using a similar keyword \texttt{dashboard}
since the document does not contain the word \texttt{dashboard}.

@@

FAQs provided by service providers are not usually considered useful
because the terms used by the people on the service are usually
different from the word that user can think of.

@@

Even finding the users' old documents can be sometimes difficult,
because people might use different keywords for the same
thing. He might try to find a file on "ZZZ" and fail, because he used
the term "WWW" before.

@@

Various techniques have been proposed to solve this vocabulary problem.
But not very successful.

Finding documents are even more difficult when
the user's mother language is different from the language used in the document.
When a user wants to find how to ``delete a file'' but the
manual of the system is written in French,
he has to \textbf{translate} the term ``delete'' and ``file''
before the search.
Non-English speakers are always having trouble
translating the word in their brain into English words
before searching on the net.

@@

The vocabulary problem and the translation problem can be solved
if the search system have a thesaurus and a translation dictionary.

For example, 
if the system knows that removing a file and deleting a file is the same,
the system can try to find something using the keyword ``delete'',
even when the user specified the keyword ``remove''.

This kind of technique is called \textit{Query expansion}, and simple query
expansion is possible if proper dictionary is provided.

@@

Query expansion is effective when simple substitution of keywords are satisfactory enough.
Using 'delete' in addition to 'remove' works...

@@

  The main idea for solving the problem is 
  providing \textbf{regular expressions} (REs)
  for  each document so that a wide variety of user queries can match one of the
  strings expanded from the REs.

@@

  People make spelling errors all the time, and approximate pattern matching algorithm
  works quite effectively for almost all search activities.
  Using the ExpandHelp algorithm, all the expressions are expanded in advance,
  so simple approximate pattern matching algorithms can be applied for the search.
  For example, a query like ``del dta'' can be used

@@

  If the author of the document does not provide the data, it would be nice if
  other users can add the ExpandHelp entries.
  This strategy is very similar to writing a hands-on document for an existing document,
  but adding ExpandHelp entries is much easier than authoring  a document from scratch.

@@

Some Unix command line tools have many options and features, and difficult to understand in many cases.
Many programmers are recently using the git version control system, but the concept of git is difficult, and
the command line options are extremely complicated.
The total number of git manuals on unix is .....

We created the GitHelp system using {\ES}, so that git users can easily
remember command options and use it without perfectly remembering the git commands.

We implemented the HelpLine system
with which a user can translate his vague intention in various languages
into a complete {\GIT} command
using the {\ES} framework.

@@

If HelpLine is installed,
the user can type a special shortcut key
(e.g. \texttt{Ctrl-J})
to invoke HelpLine after typing \sqtt{git RE 2} to see how he can
perform the task.

@@

OmniSearch is an implementation of ExpandSearch that runs on Chrome browser.
The URL window on Chrome is called omnibox,

@@

Figure xxx shows an example {\HF} page that supports finding FAQs
for PayPay Free market run by Yahoo! Japan.
We provide the description on the Scrapbox wiki service,

% https://paypayfleamarket.yahoo.co.jp/help/

\begin{figure}[H]
  \centering
  \includegraphics[width=10cm,bb=0 0 1716 1312]{figures/3d964512606a5e25646104a738ab104e.png}
  \caption{PayPay Freemarket}
  \Description{PayPay}
\end{figure}

@@

A flexible search mechanism ``ExpandSearch'' is used in HelpLine.
%
The database used in ExpandSearch are provided as a set of data entries
consisting of a regular expression that represents description of the data entry
and a corresponding command pattern string.
A description string is used to produce natural language texts
that are easily understandable by users,
while command patterns represents the generated command string
corresponding to the description.
%
For example, a help entry for showing the difference between
current file and older file can be defined like this:

@@

\paragraph{Applications of ExpandHelp}

>>>>

  We have been using this document expansion technique called
  {\ES} for several years, and the system is working on various
  commercial Web services. In this paper, we describe the idea and
  implementation of {\ES} and show how it works in the wild.
\end{abstract}

@@

People are frequently searching information using keywords on Google
and other systems.
But keyword search is still not an easy task,
because it is fundamentally difficulto to find appropriate information
that does not contain the keyword given by the user.

@@

The help system of MacOS (Catalina v10.15.5) cannot tell us how to remove a file.

\begin{figure}[H]
  \centering
  \includegraphics[width=12cm,bb=0 0 1290 1090]{figures/eaa80e41ddc3d3620fae133007274573.png}
  \caption{Asking the help application on Mac how to remove a file.}
  \Description{Mac Mac}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=12cm,bb=0 0 1310 1090]{figures/0cd679128d8f69eb2a8a966d6466a8a4.png}
  \caption{Mac}
  \Description{Mac Mac}
\end{figure}

We can get this kind of information fairly easily using search systems on the net,
so many people prefer getting information using search engines rather than
using help systems provided by manufacturers.

We can find information on Google because there are tremendous information
that describe how to ``remove a file'' on Mac.
If there are documens that contain ``remove'', ``file'', and ``Mac'',
finding such documents are not difficult.
That seems to be the main reason why people are satisfied with search engines
for finding popular information.

@@

On the other hand,
finding a less popular information is rather difficult,
because not enough documents related to the topic is found on the net.
%
If there is only one document on the net
that describes the \texttt{console} feature of a minor system \texttt{xxxxx},
people cannot find the document using a similar keyword \texttt{dashboard}
since the document does not contain the word \texttt{dashboard}.

@@

FAQs (frequently asked questions) provided by service providers are
usually not considered useful
because the terms used by the people on the service are usually
different from the keywords that user can imagine.

@@

Even finding the users' old documents can be sometimes difficult,
because people might use different keywords for the same thing case by case.
He might try to find a file related to ``IUI'' and fail, because he used
the term ``intelligent user interface'' for the file name.
%
Various techniques have been proposed to solve this vocabulary problem,
but not very successful enough.

@@

Finding documents are even more difficult when
the user's mother language is different from the language used in the document.
When a user wants to find how to ``delete a file'' but the
manual of the system is written in French,
he has to translate the term ``delete'' and ``file'' into French
before the search.
Non-English speakers are always having trouble
translating the word in their brain into English words
before searching information, because important information are
usually provided in English.

@@

% Query expansion (QE) is the process of reformulating a given query to
% improve retrieval performance in information retrieval operations,
% particularly in the context of query understanding.[1] In the context
% of search engines, query expansion involves evaluating a user's input
% (what words were typed into the search query area, and sometimes other
% types of data) and expanding the search query to match additional
% documents. Query expansion involves techniques such as:
% 
% * Finding synonyms of words, and searching for the synonyms as well
% * Finding semantically related words (e.g. antonyms, meronyms, hyponyms, hypernyms)
% * Finding all the various morphological forms of words by stemming each word in the search query
% * Fixing spelling errors and automatically searching for the corrected form or suggesting it in the results
% * Re-weighting the terms in the original query
%
% Query expansion is a methodology studied in the field of computer
% science, particularly within the realm of natural language processing
% and information retrieval.

The vocabulary problem and the translation problem can be solved
if the search system have a thesaurus and a translation dictionary.
%
For example, 
if the system knows that removing a file and deleting a file is the same,
the system can try to find something using the keyword ``delete'',
even when the user specified the keyword ``remove''.
%
This kind of technique is called ``\textit{Query expansion}'', and simple query
expansion is possible if proper dictionary is provided.

@@

Query expansion is effective when simple substitution of keywords are satisfactory enough.
In the previous example, using the keyword ``delete'' in addition to ``remove'' works
for finding the manual entry.

@@

  Our main idea for solving the problem is 
  providing regular expressions (REs)
  for  each document so that a wide variety of user queries can match one of the
  strings expanded from the REs.

@@

  People make spelling errors all the time, and approximate pattern matching algorithm
  works quite effectively for almost all search activities.
  Using the ExpandSearch algorithm, all the expressions are expanded in advance,
  so simple approximate pattern matching algorithms can be applied for the search.
  For example, a query like ``del dta'' can be used

@@

  If the author of the document does not provide the data, it would be nice if
  other users can add the {\ES} entries.
  This strategy is very similar to writing a hands-on document for an existing document,
  but adding {\ES} entries is much easier than authoring  a document from scratch.

@@

Some Unix command line tools have many options and features that are difficult to remember.
Many programmers are recently using the git version control system,
but the concept of git is difficult, and
the command line options are extremely complicated.
The total number of git manuals on unix is xxxxx lines.

We created the {\HL} system using {\ES}, so that git users can easily
remember command options and use it without perfectly remembering the git commands.

We implemented the {\HL} system
with which a user can translate his vague intention in various languages
into a complete {\GIT} command
using the {\ES} framework.

@@

If {\HL} is installed,
the user can type a special shortcut key
(e.g. \texttt{Ctrl-J})
to invoke {\HL} after typing \sqtt{git RE 2} to see how he can
perform the task.

@@

OmniSearch is an implementation of {\ES} that runs on Chrome browser.
The URL window on Chrome is called omnibox,

@@

Figure \ref{paypayhf} shows an example {\HF} page that supports finding FAQs
for ``PayPay Free Market'' run by Yahoo! Japan\footnote{
  \ssf{https:{\slash}{\slash}paypayfleamarket.yahoo.co.jp{\slash}help{\slash}}
}.

% We provide the description on the Scrapbox wiki service,

\begin{figure}[H]
  \centering
  \includegraphics[width=10cm,bb=0 0 1716 1312]{figures/3d964512606a5e25646104a738ab104e.png}
  \caption{PayPay Freemarket}
  \label{paypayhf}
  \Description{PayPay}
\end{figure}

ものすごく問いあわせが減った

@@

A flexible search mechanism ``{\ES}'' is used in {\HL}.
%
The database used in {\ES} are provided as a set of data entries
consisting of a regular expression that represents description of the data entry
and a corresponding command pattern string.
A description string is used to produce natural language texts
that are easily understandable by users,
while command patterns represents the generated command string
corresponding to the description.
%
For example, a help entry for showing the difference between
current file and older file can be defined like this:

@@

\paragraph{Applications of ExpandSearch}
